---
title: "Salmon Escapement"
author: "Jim Magdanz/Jen"
date: "October 17, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
```

#Sources

Daily escapements: [Alaska Department of Fish and Game. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1TX3CKH](http://doi:10.5063/F1TX3CKH)

Escapement Goals: [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](http://doi:10.5063/F1TQ5ZRG)

# Prepare Daily Escapement Data

```{r}
esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"), stringsAsFactors = FALSE)

head(esc)
```

`
help summarize

```{r}
esc_BB <- esc %>%
  filter(SASAP.Region == "Bristol Bay") %>% 
  group_by(Location) %>% 
  summarise(count = sum(DailyCount))

head(esc_BB)
```



# Prepare Escapment Goal Data




#Evaluate EScapement

https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e