---
title: "Salmon Escapement"
author: "Jim Magdanz/Jen"
date: "October 17, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
```

#Sources

Daily escapements: [Alaska Department of Fish and Game. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1TX3CKH](http://doi:10.5063/F1TX3CKH)

Escapement Goals: [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](http://doi:10.5063/F1TQ5ZRG)

# Prepare Daily Escapement Data

```{r}
esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"), stringsAsFactors = FALSE)

head(esc)
```



```{r}
esc_BB <- esc %>%
  filter(SASAP.Region == "Bristol Bay", Species == "Sockeye") %>% 
  separate(sampleDate, c("Year", "Month", "Day"), "-", remove=F) %>% 
  group_by(SASAP.Region, Location, Year, Species) %>% 
  summarise(AnnualCount = sum(DailyCount))

esc_BB
```



# Prepare Escapment Goal Data

```{r}

goals <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92014.1", method = "libcurl"), stringsAsFactors = FALSE)

head(goals)


```

```{r}

goals_BB <- goals %>%
  filter(Species=="Sockeye", Region == "Bristol Bay", Lower != "eliminated") %>%
  select(Species, Region, System, Lower, Upper, Type, Initial.Year) %>%
  mutate(Lower = as.numeric(Lower), Initial.Year = as.numeric(Initial.Year)) %>% 
  group_by(System)

goals_BB
```

# Join Tables

```{r}

eval <- left_join(esc_BB, goals_BB, by = c("Location" = "System")) %>% 
  mutate(Lower.Goal.Exceeded = if_else(AnnualCount > Lower,TRUE,FALSE),
         Upper.Goal.Exceeded = if_else(AnnualCount > Upper,TRUE,FALSE),
         Goal.Met = if_else(AnnualCount >Lower & AnnualCount < Upper, TRUE,FALSE)) %>% 
  select(Region, Location, Year, Species.x, Lower, Upper, Type, AnnualCount, Goal.Met, Lower.Goal.Exceeded, Upper.Goal.Exceeded)
  

head(eval)


```






# Evaluate EScapement

